---
title: "How to write more and more letters, in a triangle"
author: "Zhuang Liu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to write more and more letters, in a triangle}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
# replace this with your package name
library(raukrBest)

```


# The greatest package for a very specific purpose

If you thought that it was impossible to write letters
alphabetically from top to bottom with each number represented
the same number of times asits position in the alphabet
 - think again!

This package and its sole function, trianguletter, solves just this problem!

But you do not have to take my word for it, see for yourself:
```{r,echo=T}
# With just a simple number we specify how long into the alphabet we go.
trianguletter(10)

# Also, this package has this random dataset:
mycolors
```

# Future plans

We plan do add features so that you can give it
a letter, rather than a number, and output a
bunch of numbers instead!

